Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2015-04-20 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
Adding biographies with photos.
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4597 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

>>>>

% ----- BIOGRAPHY ------------------
% \vspace{-2in}
\vfill
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{enasiri}}]{Ehsan Nasiri} received the Bachelor of Applied Science in Computer Engineering from the University of Toronto in 2012, and the M.Eng. degree in ECE from the University of Toronto in 2015. He has been a Software Engineer at Altera since 2012.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{javeed}}]{Javeed Shaikh} received the BEng degree in Electrical Engineering from McGill University in 2011 and the MEng degree in ECE from the University of Toronto in 2014. He has been a Software Engineer at Google since 2013.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{apereira}}]{Andre Hahn Pereira} is currently pursuing his B.Sc degree in ECE at the University of S\~{a}o Paulo. He was an exchange student at the University of Toronto from September 2012 until August 2013.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{vbetz}}]{Vaughn Betz}(S'88--M'91) received the B.Sc degree in EE from the University of Manitoba in 1991, the MS degree in ECE from the University of Illinois at Urbana-Champaign in 1993, and the PhD degree in ECE from the University of Toronto in 1998.

Dr. Betz was a co-founder of Right Track CAD in 1998 and VP of Engineering until its acquisition by Altera in 2000. He was at Altera from 2000 to 2011, ultimately as Senior Director of Software Engineering. He joined the University of Toronto as an Associate Professor in 2011, where his research covers FPGA architecture, CAD and FPGA-based computation.
\end{IEEEbiography}

% ----------------------------------
